Modular flow and holographic entanglement entropy in cutoff AdS / \TTbar deformed theory

### 2021-06-24 alpha/CutoffModularFlow/notes.tex
Update notes: merge upstream changes

% !TeX TS-program = pdflatex
% !BIB TS-program = biblatex

\documentclass[11pt,a4paper]{article}
\pdfoutput=1

@@

\section{Entanglement in the boundary story}

\subsection{Rindler map in finite temperature}

@@

	For simplicity, we now restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{{\tilde L}}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval. For a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
	\begin{equation}
		x_\pm = \pm \frac{{\tilde L}}{2} \cosh \theta,
	\quad
		t_\pm = \pm \frac{{\tilde L}}{2} \sinh \theta,
	\end{equation}
	Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi_\mrm{CFT} &= \frac{2\pi}{{\tilde L}} \bigg\{
			\pqty\Big{
				\pqty{
					(\tfrac{{\tilde L}}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty\Big{
				\pqty{
					(\tfrac{{\tilde L}}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{gather}
	Suppose the interval $\mcal{A}$ lies on the constant $t = 0$ slice; around the constant $t = 0$ slice, the modular flow becomes:
	\begin{equation}
		\xi_\mrm{CFT}|_{t = 0} 
		= \frac{2\pi}{{\tilde L}}
			\pqty{
				(\tfrac{{\tilde L}}{2})^2
				- x^2
			} \,\pdd{t}
	\end{equation}

@@

	Alternatively, we can re-derive the bulk modular generator from scratch by requiring that it vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
	}. See \autoref{sect:modFlowPoincare} for a detailed description. 
	Again, the overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon; we demand that the surface gravity is $2\pi$ along the RT surface:
	\begin{equation}
%		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
%	\quad
		\kappa_\xi^2
		= (2\pi)^2
		= -\frac{1}{2}\,
			(\nabla_{\mu} \xi_{\nu})
			(\nabla^{\mu} \xi^{\nu})
	\end{equation}
	Again, we restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{L_\infty}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side ${\tilde L}$. 
	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi &= \frac{2\pi}{L_\infty} \bigg\{
			\pqty\Big{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty\Big{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\\ &\qquad\qquad 
			+ \pqty\big{
				x\sinh\theta
				- t\cosh\theta
			} \,2z\pdd{z}
		\bigg\}
	\end{aligned}
	\end{gather}

	We note that the $\pdd{z}$ term vanishes in the following two cases:
	\begin{itemize}[noitemsep,topsep=0pt]
	\item as $z\to 0$, i.e.~near the asymptotic boundary;
	\item within the whole plane: $
			x\sinh\theta
			= t\cosh\theta
		$ where the RT surface lies. 
	\end{itemize}

@@

	We then consider $\xi$ evaluated at the {constant finite cutoff} $z = z_c$,
	\begin{equation}
	\begin{aligned}
		\xi|_{z=z_c}
		= \frac{2\pi}{
				L\sqrt{1 + (2z_c/L)^2}
			}
		& \bigg\{
			\pqty\Big{
				\pqty{
					(\tfrac{L}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\[-.5ex] &\quad 
			+ \pqty\Big{
				\pqty{
					(\tfrac{L}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\\ &\quad 
			+ \pqty\big{
				x\sinh\theta
				- t\cosh\theta
			} \,2z_c\pdd{z}
		\bigg\}
	\end{aligned}
	\end{equation}
	Note that the $\pdd{z}$ component is generally non-zero, i.e.~$\xi|_{z=z_c}$ is not entirely contained in the $z = z_c$ plane. 
	We observe the factor $
		\sqrt{1 + (2z_c/L)^2}
	$ which is featured prominently in the \TTbar deformed $C(L)$ function, given in \cite{Lewkowycz:2019xse}:
	\begin{equation}
		C(L) = L\,\pdd{L} S(L)
		= \frac{c}{3} 
			\frac{1}{
				\sqrt{1 + (2z_c/L)^2}
			}
	\end{equation}

	This seems nice and all but there is a subtlety for finite cutoff $z = z_c$. 
	In the bulk the constant surface gravity $
		\xi^\nu \cdv{\nu} \xi^\mu
		= \kappa_\xi \xi^\mu
		= 2\pi \xi^\mu
	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$. However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
	\begin{equation}
	\begin{aligned}
		\xi^{\mrm{FT}}_c
		\equiv \proj{\sslash} \xi|_{z_c}
		= \frac{2\pi}{
				\sqrt{1 + (2z_c/L)^2}
			}
		& \bigg\{
			\pqty\Big{
				\pqty{
					(\tfrac{L}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\[-2ex] &\quad 
			+ \pqty\Big{
				\pqty{
					(\tfrac{L}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{equation}
	Which no longer has normalized $\beta$ if $z_c \ne 0$. In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $
		\frac{L}{L_\infty}
		= 1/\sqrt{1 + (2z_c/L)^2}
	$, which means that:
	\begin{equation}
		\beta^{\mrm{FT}}_c
		= \sqrt{1 + (2z_c/L)^2}
		\sim 1 + 2z_c^2 / L^2
	\end{equation}

@@

	We can further replace the flow parameter $\lambda$ with time coordinate $t$ by considering $
		\dd{z}/\dd{t}
		= {\dv{z}{\lambda}}/{\dv{t}{\lambda}}
	$, which leads to the following equations:
	\begin{equation}
		\dv{z}{t}
		= \frac{2tz}{\alpha z^2 + t^2 - (L_\infty/2)^2},
	\quad
		\alpha = 1 + \frac{x_c^2}{z_c^2},
	\quad
		\frac{x}{x_c} = \frac{z}{z_c}
	\end{equation}
	The solution is then given by:
	\begin{equation}
		z = z(t;x_c,z_c)
		= \frac{
				(L_\infty/2)^2 + \alpha z_c^2
				- \sqrt{
					\pqty\big{(L_\infty/2)^2 - \alpha z_c^2}^2
					+ 4t^2 \alpha z_c^2
				}
			}{2\alpha z_c}
	\end{equation}

@@

	Now we consider constant cutoff at $r = r_c$. Again we need to trade the $L_\infty$ above with the coordinate length of the interval $L$ at the cutoff $r_c$. The relation can be solved by looking at the geodesic equation, which is slightly non-trivial this time:
	\begin{equation}
		\frac{\cosh L_\infty T}{\cosh LT}
		= \frac{r_c}{\sqrt{r_c^2 - 4T^2}}
	\end{equation}
	\begin{equation}
		r(\phi) = \frac{2T\cosh TL}{
				\sqrt{\cosh^2 TL - \pqty\big{
					1 - \frac{4T^2}{r_c^2}
				}\cosh^2 2T\phi}
			}
	\end{equation}
	We then compute the charges like before, and we have:
	\begin{equation}
		\var{Q}_\xi
		= \frac{\var{T}}{2G} \pqty{
				L \coth LT - \frac{1}{T}
			}
			\frac{1}{\sqrt{
				1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
			}}
	\end{equation}

@@

	We now restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{L_\infty}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
	\begin{equation}
		x_\pm = \pm \frac{L_\infty}{2} \cosh \theta,
	\quad
		t_\pm = \pm \frac{L_\infty}{2} \sinh \theta,
	\end{equation}
	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi &= \frac{2\pi}{L_\infty} \bigg\{
			\pqty\Big{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty\Big{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\\ &\qquad\qquad 
			+ \pqty\big{
				x\sinh\theta
				- t\cosh\theta
			} \,2z\pdd{z}
		\bigg\}
	\end{aligned}
	\end{gather}

	We note that the $\pdd{z}$ term vanishes in the following two cases:
	\begin{itemize}[noitemsep,topsep=0pt]
	\item as $z\to 0$, i.e.~near the asymptotic boundary;
	\item within the whole plane: $
			x\sinh\theta
			= t\cosh\theta
		$ where the RT surface lies. 
	\end{itemize}

>>>>

% !TeX encoding = UTF-8
% !TeX TS-program = pdflatex
% !BIB TS-program = biblatex

\documentclass[11pt,a4paper,utf8]{article}

\ifdefined\pdfoutput
	\pdfoutput=1
\fi

@@

\section{Entanglement in the boundary story}
\subsection{Review of entanglement at zero temperature}

\subsection{Entanglement entropy at finite temperature}

@@

	For simplicity, we now restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{{\tilde L}}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval. For a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
	\begin{equation}
		x_\pm = \pm \frac{{\tilde L}}{2} \cosh \theta,
	\quad
		t_\pm = \pm \frac{{\tilde L}}{2} \sinh \theta,
	\end{equation}
	Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi_\mrm{CFT} &= \frac{2\pi}{{\tilde L}} \bigg\{
			\pqty{
				\pqty{
					(\tfrac{{\tilde L}}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty{
				\pqty{
					(\tfrac{{\tilde L}}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{gather}
	Suppose the interval $\mcal{A}$ lies on the constant $t = 0$ slice; around the constant $t = 0$ slice, the modular flow becomes:
	\begin{equation}
		\xi_\mrm{CFT}|_{t = 0} 
		= \frac{2\pi}{{\tilde L}}
			\pqty{
				(\tfrac{{\tilde L}}{2})^2
				- x^2
			} \,\pdd{t}
	\end{equation}

@@

	Alternatively, we can re-derive the bulk modular generator from scratch by requiring that it vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
	}. See \autoref{sect:modFlowPoincare} for a detailed description. 
	Again, the overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon; we demand that the surface gravity is $2\pi$ along the RT surface:
	\begin{equation}
%		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
%	\quad
		\kappa_\xi^2
		= (2\pi)^2
		= -\frac{1}{2}\,
			(\nabla_{\mu} \xi_{\nu})
			(\nabla^{\mu} \xi^{\nu})
	\end{equation}
	Again, we restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{L_\infty}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side ${\tilde L}$. 
	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface.

	{\color{red} use $l_u,\,l_v$}

	We have:
	\begin{gather}
	\begin{aligned}
		\xi &= \frac{2\pi}{L_\infty} \bigg\{
			\pqty{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\\ &\qquad\qquad 
			+ \pqty{
				x\sinh\theta
				- t\cosh\theta
			} \,2z\pdd{z}
		\bigg\}
	\end{aligned}
	\end{gather}

The RT surface is the set of the fixed points of the modular flow, ....bifurcating surface....

\eq{ &\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta =0\\
			&	x\sinh\theta
				- t\cosh\theta
				}

	We note that the $\pdd{z}$ term vanishes in the following two cases:
	\begin{itemize}%[noitemsep,topsep=0pt]
	\item as $z\to 0$, i.e.~near the asymptotic boundary;
	\item within the whole plane: $
			x\sinh\theta
			= t\cosh\theta
		$ where the RT surface lies. 
	\end{itemize}

@@

\begin{comment}
	We then consider $\xi$ evaluated at the {constant finite cutoff} $z = z_c$,
	\begin{equation}
	\begin{aligned}
		\xi|_{z=z_c}
		= \frac{2\pi}{
				L\sqrt{1 + (2z_c/L)^2}
			}
		& \bigg\{
			\pqty{
				\pqty{
					(\tfrac{L}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\[-.5ex] &\quad 
			+ \pqty{
				\pqty{
					(\tfrac{L}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\\ &\quad 
			+ \pqty{
				x\sinh\theta
				- t\cosh\theta
			} \,2z_c\pdd{z}
		\bigg\}
	\end{aligned}
	\end{equation}
	Note that the $\pdd{z}$ component is generally non-zero, i.e.~$\xi|_{z=z_c}$ is not entirely contained in the $z = z_c$ plane. 
	We observe the factor $
		\sqrt{1 + (2z_c/L)^2}
	$ which is featured prominently in the \TTbar deformed $C(L)$ function, given in \cite{Lewkowycz:2019xse}:
	\begin{equation}
		C(L) = L\,\pdd{L} S(L)
		= \frac{c}{3} 
			\frac{1}{
				\sqrt{1 + (2z_c/L)^2}
			}
	\end{equation}
\end{comment}

	This seems nice and all but there is a subtlety for finite cutoff $z = z_c$. 
	In the bulk the constant surface gravity $
		\xi^\nu \cdv{\nu} \xi^\mu
		= \kappa_\xi \xi^\mu
		= 2\pi \xi^\mu
	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$. However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:

	{\color{red} delete
	\begin{equation}
	\begin{aligned}
		\xi^{\mrm{FT}}_c
		\equiv \proj{\text{/\!/}} \xi|_{z_c}
		= \frac{2\pi}{
				\sqrt{1 + (2z_c/L)^2}
			}
		& \bigg\{
			\pqty{
				\pqty{
					(\tfrac{L}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\[-2ex] &\quad 
			+ \pqty{
				\pqty{
					(\tfrac{L}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{equation}
	Which no longer has normalized $\beta$ if $z_c \ne 0$.
}

	 In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $
		\frac{L}{L_\infty}
		= 1/\sqrt{1 + (2z_c/L)^2}
	$, which means that:
	\begin{equation}
		\beta^{\mrm{FT}}_c
		= \sqrt{1 + (2z_c/L)^2}
		\sim 1 + 2z_c^2 / L^2
	\end{equation}

@@

	We can further replace the flow parameter $\lambda$ with time coordinate $t$ by considering $
		\dd{z}/\dd{t}
		= {\dv{z}{\lambda}}/{\dv{t}{\lambda}}
	$, which leads to the following equations:
	\begin{equation}
		\dv{z}{t}
		= \frac{2tz}{\alpha z^2 + t^2 - (L_\infty/2)^2},
	\quad
		\alpha = 1 + \frac{x_c^2}{z_c^2},
	\quad
		\frac{x}{x_c} = \frac{z}{z_c}
	\end{equation}
	The solution is then given by:
	\begin{equation}
		z = z(t;x_c,z_c)
		= \frac{
				(L_\infty/2)^2 + \alpha z_c^2
				- \sqrt{
					\pqty{(L_\infty/2)^2 - \alpha z_c^2}^2
					+ 4t^2 \alpha z_c^2
				}
			}{2\alpha z_c}
	\end{equation}

@@

	Now we consider constant cutoff at $r = r_c$. Again we need to trade the $L_\infty$ above with the coordinate length of the interval $L$ at the cutoff $r_c$. The relation can be solved by looking at the geodesic equation, which is slightly non-trivial this time:
	\begin{equation}
		\frac{\cosh L_\infty T}{\cosh LT}
		= \frac{r_c}{\sqrt{r_c^2 - 4T^2}}
	\end{equation}
	\begin{equation}
		r(\phi) = \frac{2T\cosh TL}{
				\sqrt{\cosh^2 TL - \pqty{
					1 - \frac{4T^2}{r_c^2}
				}\cosh^2 2T\phi}
			}
	\end{equation}
	We then compute the charges like before, and we have:
	\begin{equation}
		\var{Q}_\xi
		= \frac{\var{T}}{2G} \pqty{
				L \coth LT - \frac{1}{T}
			}
			\frac{1}{\sqrt{
				1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
			}}
	\end{equation}

@@

	We now restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{L_\infty}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
	\begin{equation}
		x_\pm = \pm \frac{L_\infty}{2} \cosh \theta,
	\quad
		t_\pm = \pm \frac{L_\infty}{2} \sinh \theta,
	\end{equation}
	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi &= \frac{2\pi}{L_\infty} \bigg\{
			\pqty{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty{
				\pqty{
					(\tfrac{L_\infty}{2})^2 - z^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\\ &\qquad\qquad 
			+ \pqty{
				x\sinh\theta
				- t\cosh\theta
			} \,2z\pdd{z}
		\bigg\}
	\end{aligned}
	\end{gather}

	We note that the $\pdd{z}$ term vanishes in the following two cases:
	\begin{itemize}%[noitemsep,topsep=0pt]
	\item as $z\to 0$, i.e.~near the asymptotic boundary;
	\item within the whole plane: $
			x\sinh\theta
			= t\cosh\theta
		$ where the RT surface lies. 
	\end{itemize}
